HTML tests

### 2022-07-28 Dashboard/NGO Analysis dashboard alpha v002.Rmd
Fixing the currency test.

  # Data frames ================================================================
  ## Creating data frame from html file-----------------------------------------
  htmldata <- reactive({
    # validating file
    validate(need(
      tools::file_ext(input$html$datapath) == "html",
      "Please upload an html file."
    ))

@@

@@

  ## Currency scale-------------------------------------------------------------
  # Reactive function to check for currency and use currency code or ?
  currency_scale <- reactive({
    scale_y_continuous(
      # Checking for uniform currency code
      labels = ifelse(length(unique(htmldata()$valutakode)) == 1,
        # Using the currency code if uniform
        label_dollar(prefix = str_c(htmldata()$valutakode[1], " ")),
        # alternative prefix if multiple currencies in the data
        label_dollar(prefix = "? ")
      )
    )
  })

  ## Plotly caption-------------------------------------------------------------
  # Reactive function to create plotly caption (ggplot captions and subtitles
  # are lost in the conversion) (shamelessly stolen from the Internet, with
  # minor modifications).
  # Checks for uniform currency code and prints a warning
  # if there are multiple currency codes.
  plotly_caption <- reactive({
    list(
      x = 1, y = -0.1, text = ifelse(length(unique(htmldata()$valutakode)) == 1,
        "", "Note: not all values are denominated in the same currency"
      ),
      showarrow = F, xref = "paper", yref = "paper",
      xanchor = "right", yanchor = "auto", xshift = 0, yshift = 0,
      font = list(size = 11)
    )
  })

@@

  # Testing if the correct years have been entered
  if (as.character(all_of(start)) %in% names(htmlready) &&
    as.character(all_of(end)) %in% names(htmlready)) {
    # Creating the data frame
    read_proff(file, start, end)
  } else {
    validate("Please ensure you have entered the correct start and end years.")
  }
}

read_proff <- function(file, start, end) {
  read_html(file, encoding = "UTF-8") |>
    html_node("#inner-frame") |>
    html_table() |>
    # removing empty column, using all_of(argument)
    select(
      REGNSKAPSPERIODE:all_of(start)
    ) |>
    # removing white space
    mutate(
      REGNSKAPSPERIODE = str_squish(REGNSKAPSPERIODE)
    ) |>
    # removing duplicate table sometimes created by read_html()
    filter(
      !row_number() > 176
    ) |>
    # removing duplicate rows
    filter(
      !grepl("Lukk", REGNSKAPSPERIODE)
    ) |>
    # tidying data using pivot_longer() and all_of(argument)
    pivot_longer(
      all_of(end):all_of(start),
      names_to = "year"
    ) |>
    # creating a currency code column and turning current currency codes into
    # NAs
    mutate(
      # changing to real NAs
      value = na_if(value, "-"),
      # turning years into numbers
      year = as.integer(year),
      # creating a currency code column and turning current currency codes into
      # NAs
      valutakode = ifelse(REGNSKAPSPERIODE == "Valutakode", value, NA)
    ) |>
    # filling the currency column
    fill(
      valutakode,
      .direction = "updown"
    ) |>
    # removing dates and redundant currency
    filter(
      REGNSKAPSPERIODE != "Sluttdato" & REGNSKAPSPERIODE != "Startdato" &
        REGNSKAPSPERIODE != "Valutakode"
    ) |>
    mutate(
      # removing white space in numbers
      value = str_replace_all(value, "\\s", ""),
      # turning numbers into true numbers
      value = as.numeric(value),
      # removing values that are years
      value = ifelse(grepl("i hele 1000", REGNSKAPSPERIODE), NA, value)
    ) |>
    # removing any remaining duplicate rows
    distinct() |>
    # pivoting to create 'tidy' variables
    pivot_wider(
      names_from = REGNSKAPSPERIODE, values_from = value
    ) |>
    # tidying names
    clean_names() |>
    # removing headings from the table
    select(
      -lederlonn_i_hele_1000,
      -resultatregnskap_i_hele_1000,
      -balanseregnskap_i_hele_1000
    ) |>
    # making it clear what lonn refers to
    rename(
      lederlonn = lonn
    ) |>
    # Creating new variables for plots
    mutate(
      annual_profit = ifelse(arsresultat >= 0, TRUE, FALSE),
      balance_positive = ifelse(sum_egenkapital_og_gjeld >= 0, TRUE, FALSE)
    ) |>
    # arranging by year for practical display
    arrange(desc(year))
}

>>>>

  # Data frames ================================================================
  ## Creating data frame from html file-----------------------------------------
  html_currency <- reactive({
    # validating file
    validate(need(
      tools::file_ext(input$html$datapath) == "html",
      "Please upload an html file."
    ))

@@

  htmldata <- reactive({
    read_proff_two(html_currency())
  })

@@

  ## Currency scale-------------------------------------------------------------
  # Reactive function to check for currency and use currency code or ?
  currency_scale <- reactive({
    scale_y_continuous(
      # Checking for uniform currency code
      labels = ifelse(length(unique(html_currency()$valutakode)) == 1,
        # Using the currency code if uniform
        label_dollar(prefix = str_c(unique(html_currency()$valutakode), " ")),
        # alternative prefix if multiple currencies in the data
        label_dollar(prefix = "? ")
      )
    )
  })

  ## Plotly caption-------------------------------------------------------------
  # Reactive function to create plotly caption (ggplot captions and subtitles
  # are lost in the conversion) (shamelessly stolen from the Internet, with
  # minor modifications).
  # Checks for uniform currency code and prints a warning
  # if there are multiple currency codes.
  plotly_caption <- reactive({
    list(
      x = 1, y = -0.1, text = ifelse(length(unique(html_currency()$valutakode)) == 1,
        "", "Note: not all values are denominated in the same currency"
      ),
      showarrow = F, xref = "paper", yref = "paper",
      xanchor = "right", yanchor = "auto", xshift = 0, yshift = 0,
      font = list(size = 11)
    )
  })

@@

  # Testing if the correct years have been entered
  if (as.character(all_of(start)) %in% names(htmlready) &&
    as.character(all_of(end)) %in% names(htmlready)) {
    # Creating the data frame
    read_proff_one(htmltable, start, end)
  } else {
    validate("Please ensure you have entered the correct start and end years.")
  }
}

read_proff_one <- function(object, start, end) {
    object |> 
  # removing empty column, using all_of(argument)
    select(
      REGNSKAPSPERIODE:all_of(start)
    ) |>
    # removing white space
    mutate(
      REGNSKAPSPERIODE = str_squish(REGNSKAPSPERIODE)
    ) |>
    # removing duplicate table sometimes created by read_html()
    filter(
      !row_number() > 176
    ) |>
    # removing duplicate rows
    filter(
      !grepl("Lukk", REGNSKAPSPERIODE)
    ) |>
    # tidying data using pivot_longer() and all_of(argument)
    pivot_longer(
      all_of(end):all_of(start),
      names_to = "year"
    ) |>
    # creating a currency code column and turning current currency codes into
    # NAs
    mutate(
      # changing to real NAs
      value = na_if(value, "-"),
      # turning years into numbers
      year = as.integer(year),
      # creating a currency code column and turning current currency codes into
      # NAs
      valutakode = ifelse(REGNSKAPSPERIODE == "Valutakode", value, NA)
    ) |> 
    fill(
      valutakode,
      .direction = "downup"
    )
}

read_proff_two <- function(object) {
     object |>
    # removing dates and redundant currency
    select(-valutakode) |> 
    filter(
      REGNSKAPSPERIODE != "Sluttdato" & REGNSKAPSPERIODE != "Startdato" &
        REGNSKAPSPERIODE != "Valutakode"
    ) |>
    mutate(
      # removing white space in numbers
      value = str_replace_all(value, "\\s", ""),
      # turning numbers into true numbers
      value = as.numeric(value),
      # removing values that are years
      value = ifelse(grepl("i hele 1000", REGNSKAPSPERIODE), NA, value)
    ) |>
    # removing any remaining duplicate rows
    distinct() |>
    # pivoting to create 'tidy' variables
    pivot_wider(
      names_from = REGNSKAPSPERIODE, values_from = value
    ) |>
    # tidying names
    clean_names() |>
    # removing headings from the table
    select(
      -lederlonn_i_hele_1000,
      -resultatregnskap_i_hele_1000,
      -balanseregnskap_i_hele_1000
    ) |>
    # making it clear what lonn refers to
    rename(
      lederlonn = lonn
    ) |>
    # Creating new variables for plots
    mutate(
      annual_profit = ifelse(arsresultat >= 0, TRUE, FALSE),
      balance_positive = ifelse(sum_egenkapital_og_gjeld >= 0, TRUE, FALSE)
    ) |>
    # arranging by year for practical display
    arrange(desc(year))
}

### 2022-07-28 Old/Shiny/Test/HTML tests.Rmd
Fixing the currency test.

```{r}
read_proff <- function(file, start, end) {
  read_html(file, encoding = "UTF-8") |>
    html_node("#inner-frame") |>
    html_table() |>
    # removing empty column, using all_of(argument)
    select(
      REGNSKAPSPERIODE:all_of(start)
    ) |>
    # removing white space
    mutate(
      REGNSKAPSPERIODE = str_squish(REGNSKAPSPERIODE)
    ) |>
    # removing duplicate table sometimes created by read_html()
    filter(
      !row_number() > 176
    ) |>
    # removing duplicate rows
    filter(
      !grepl("Lukk", REGNSKAPSPERIODE)
    ) |>
    # tidying data using pivot_longer() and all_of(argument)
    pivot_longer(
      all_of(end):all_of(start),
      names_to = "year"
    ) |>
    # creating a currency code column and turning current currency codes into
    # NAs
    mutate(
      # changing to real NAs
      value = na_if(value, "-"),
      # turning years into numbers
      year = as.integer(year),
      # creating a currency code column and turning current currency codes into
      # NAs
      valutakode = ifelse(REGNSKAPSPERIODE == "Valutakode", value, NA)
    ) |>
    # filling the currency column

@@

    fill(
      valutakode,
      .direction = "downup"
    ) # |>
    # removing dates and redundant currency
    # filter(
    #   REGNSKAPSPERIODE != "Sluttdato" & REGNSKAPSPERIODE != "Startdato" &
    #     REGNSKAPSPERIODE != "Valutakode"
    # ) |>
    # mutate(
    #   # removing white space in numbers
    #   value = str_replace_all(value, "\\s", ""),
    #   # turning numbers into true numbers
    #   value = as.numeric(value),
    #   # removing values that are years
    #   value = ifelse(grepl("i hele 1000", REGNSKAPSPERIODE), NA, value)
    # ) |>
    # # removing any remaining duplicate rows
    # distinct() |>
    # # pivoting to create 'tidy' variables
    # pivot_wider(
    #   names_from = REGNSKAPSPERIODE, values_from = value
    # ) |>
    # # tidying names
    # clean_names() |>
    # # removing headings from the table
    # select(
    #   -lederlonn_i_hele_1000,
    #   -resultatregnskap_i_hele_1000,
    #   -balanseregnskap_i_hele_1000
    # ) |>
    # # making it clear what lonn refers to
    # rename(
    #   lederlonn = lonn
    # ) |>
    # # Creating new variables for plots
    # mutate(
    #   annual_profit = ifelse(arsresultat >= 0, TRUE, FALSE),
    #   balance_positive = ifelse(sum_egenkapital_og_gjeld >= 0, TRUE, FALSE)
    # ) |>
    # # arranging by year for practical display
    # arrange(desc(year))
}

@@

@@

>>>>

```{r}
read_proff_one <- function(file, start, end) {
  read_html(file, encoding = "UTF-8") |>
    html_node("#inner-frame") |>
    html_table() |>
    # removing empty column, using all_of(argument)
    select(
      REGNSKAPSPERIODE:all_of(start)
    ) |>
    # removing white space
    mutate(
      REGNSKAPSPERIODE = str_squish(REGNSKAPSPERIODE)
    ) |>
    # removing duplicate table sometimes created by read_html()
    filter(
      !row_number() > 176
    ) |>
    # removing duplicate rows
    filter(
      !grepl("Lukk", REGNSKAPSPERIODE)
    ) |>
    # tidying data using pivot_longer() and all_of(argument)
    pivot_longer(
      all_of(end):all_of(start),
      names_to = "year"
    ) |>
    # creating a currency code column and turning current currency codes into
    # NAs
    mutate(
      # changing to real NAs
      value = na_if(value, "-"),
      # turning years into numbers
      year = as.integer(year),
      # creating a currency code column and turning current currency codes into
      # NAs
      valutakode = ifelse(REGNSKAPSPERIODE == "Valutakode", value, NA)
    ) |> 
    fill(
      valutakode,
      .direction = "downup"
    )
}

@@

read_proff_two <- function(object) {
     object |>
    # removing dates and redundant currency
    select(-valutakode) |> 
    filter(
      REGNSKAPSPERIODE != "Sluttdato" & REGNSKAPSPERIODE != "Startdato" &
        REGNSKAPSPERIODE != "Valutakode"
    ) |>
    mutate(
      # removing white space in numbers
      value = str_replace_all(value, "\\s", ""),
      # turning numbers into true numbers
      value = as.numeric(value),
      # removing values that are years
      value = ifelse(grepl("i hele 1000", REGNSKAPSPERIODE), NA, value)
    ) |>
    # removing any remaining duplicate rows
    distinct() |>
    # pivoting to create 'tidy' variables
    pivot_wider(
      names_from = REGNSKAPSPERIODE, values_from = value
    ) |>
    # tidying names
    clean_names() |>
    # removing headings from the table
    select(
      -lederlonn_i_hele_1000,
      -resultatregnskap_i_hele_1000,
      -balanseregnskap_i_hele_1000
    ) |>
    # making it clear what lonn refers to
    rename(
      lederlonn = lonn
    ) |>
    # Creating new variables for plots
    mutate(
      annual_profit = ifelse(arsresultat >= 0, TRUE, FALSE),
      balance_positive = ifelse(sum_egenkapital_og_gjeld >= 0, TRUE, FALSE)
    ) |>
    # arranging by year for practical display
    arrange(desc(year))
}

@@

read_proff_two(test)

@@

```{r}
?validate
```
